---
name: Samuel
surname: Verevis
position: "Economist"
address: "Ministry of Foreign Affairs and Trade"
phone: +64 278 419 295
email: "Sam.john.vs@gmail.com"
github: Samueljvs
linkedin: Samuel Verevis
www: samueljvs.netlify.app/
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 009ACD 
output: vitae::awesomecv
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

  library(vitae)     # The CV's LaTeX Template
  library(tibble)    # Data structure for tribbles
  library(magrittr)  # The Pipe %>%
  library(here)      # Relative File Paths
  library(readr)     # Data Loading
  library(glue)      # String Manipulation
  library(emojifont)
  library(fontawesome)
  
  source(file = here("r","data.r"))

# old color: ef4089
# profilepic: sam.jpg
  
```

# Career Summary

```{r EMPLOYMENT}
work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} --- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

# Education

```{r EDUCATION}
edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{startYear} -- {endYear}",.na = ""),
    where = where
  )
```

# Skills

```{r SKILLS}
skills %>%
  detailed_entries(
    with = area,
    what = level,
    why = skills
  )
```

<!-- # Notable Projects -->

<!-- ```{r PROJECTS} -->
<!-- projects %>% -->
<!--   detailed_entries( -->
<!--     with = area, -->
<!--     what = sub, -->
<!--     why = detail -->
<!--   ) -->
<!-- ``` -->
 
# Research Papers

\descriptionstyle{
 S. Verevis, M. Ungor, 2020. `What Has New Zealand Gained from the FTA with China?: A Counterfactual Analysis'} \hspace*{\fill}[\faLink](https://onlinelibrary.wiley.com/doi/epdf/10.1111/sjpe.12260)

\descriptionstyle{ 
S. Verevis, T. Maloney, 2020. 'Estimating the Ministry of Social Development Gender Pay Gap (Internal)'}

\descriptionstyle{
MFAT Working Paper, February 2022. 'Inclusive and productive characteristics of New Zealands goods export firms'}\hspace*{\fill}[\faDownload](https://www.mfat.govt.nz/assets/Trade-General/Trade-stats-and-economic-research/Inclusive-and-productive-characteristics-of-New-Zealand-goods-exporting-firms-MFAT-Working-Paper.pdf)

\descriptionstyle{
MFAT Working Paper, May 2021. 'The Productive, Sustainable  and Inclusive Trade Channels Framework'}\hspace*{\fill}[\faDownload](https://www.mfat.govt.nz/assets/Trade-General/Trade-stats-and-economic-research/Productive-Sustainable-and-Inclusive-Trade-Channels-Framework.pdf)


\descriptionstyle{
MFAT Working Paper, July 2020. 'Industry Exposure to Trade - The Trade Opportunities and Risk Model'}\hspace*{\fill}[\faDownload](https://www.mfat.govt.nz/assets/Trade-General/Trade-stats-and-economic-research/STORM-Analysis-Unclassified-Version.pdf)

\descriptionstyle{
People’s Choice Poster Prize - 2018 NZAE conference}\hspace*{\fill}[\faLink](https://www.nzae.org.nz/prizes/peoples-choice-poster-prize/)

# Competitions

\descriptionstyle{
*Exploring UK's fatal Traffic Accidents* - 1st Place}  \hspace*{\fill}[\faLink](https://app.datacamp.com/workspace/w/39b1c5ff-f516-4e84-af83-04d8ea361642)

\descriptionstyle{
*Why staff are leaving and why you should care* - 1st Place}  \hspace*{\fill}[\faLink](https://app.datacamp.com/workspace/w/acce6834-78ac-4e3c-9f36-a37b6da20ffe)

\descriptionstyle{
*Neither Too much nor too little but just right. A protfolio assessment on the Goldie-locks of Bitcoin* - 2nd Place} \hspace*{\fill}[\faLink](https://app.datacamp.com/workspace/w/b4d8a09a-db18-40e4-9d74-f0b15ad38934)

\descriptionstyle{
*Hakuna Moscato. It means drink wine - A targeted approach to regional wine promotions* - 2nd Place} \hspace*{\fill}[\faLink](https://app.datacamp.com/workspace/w/9fe41f5d-25aa-44cf-9046-11c7aba12587)


# Other

```{r Other}

other %>%
  detailed_entries(
    with = area,
    what = sub,
    why = detail
  )
```

\vspace{12pt}

\descriptionstyle{
References available upon request}






